Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/introduction.tex
fix typos
Minor edit.

\xhdr{Additional findings.}
We investigate the ``first-mover advantage" phenomenon in more detail. Being first in the market gives free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. \asedit{We find that either effects alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm.}

@@

While reputation scores already introduce some noise and randomness into users' choices, we consider an alternative choice model in which the noise/randomness is explicit: a small fraction of users choose a firm uniformly at random. We confirm the theoretical intuition that better algorithms prevail if the parameters -- the ``random fraction" and the time horizon -- are sufficiently large. However, we find that this effect is negligible for some smaller but still ``relevant" parameter values.

>>>>

\xhdr{Additional findings.}
We investigate the ``first-mover advantage" phenomenon in more detail. Being first in the market gives free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. \asedit{We find that either effect alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm.}

@@

While reputation scores already introduce some noise and randomness into users' choices, we consider an alternative choice rule in which the noise/randomness is explicit: a small fraction of users choose a firm uniformly at random. We confirm the theoretical intuition that better algorithms prevail if the parameter -- \asedit{essentially, the expected number ``random users"} -- is sufficiently large. However, we find that this effect is negligible for some smaller but still ``relevant" parameter values.
